A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-11-21 paper.tex
fix numbers

\paragraph{Infinity vs Euclidean norms}
The average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.04 for 2D data, and 1.14
for 3D data. These ratios are lower than the theoretical values of
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for
random-uniform signals. Unsurprisingly, the infinity norm surpasses the
Euclidean norm in terms of resource consumption. Memory-wise, the
infinity norm requires a constant amount of 80~B, used to store the
intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
the amount of required memory increases for longer time-series, and it also increases with larger
values of $\epsilon$. Similar observations are made for the processing
time, with values ranging from 0.4~ms for the simplest time-series and
smallest $\epsilon$, to 41.3~ms for the most complex time-series and
largest~$\epsilon$.
%~ Figure~\ref{fig:memory} shows the memory consumption
%~ of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
%~ at the end of long compressed ranges where the signal was $\epsilon$-closed
%~ to the linear approximation.

\paragraph{2D vs 3D}
For a given $\epsilon$, the compression
ratios are always higher in 2D than in 3D. It makes sense since the
probability for the signal to deviate from a straight line
approximation is higher in 3D than it is in 2D. Besides, resource
consumption is higher in 3D than in 2D: for the infinity norm, 3D
consumes 1.4 times more memory than 2D (1.8 times on average for
Euclidean norm), and processing time is 1.4 longer (1.3 on
average for Euclidean norm).

>>>>

\paragraph{Infinity vs Euclidean norms}
The average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.03 for 2D data, and 1.06
for 3D data. These ratios are lower than the theoretical values of
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for
random-uniform signals. Unsurprisingly, the infinity norm surpasses the
Euclidean norm in terms of resource consumption. Memory-wise, the
infinity norm requires a constant amount of 80~B, used to store the
intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
the amount of required memory increases for longer time-series, and it also increases with larger
values of $\epsilon$. Similar observations are made for the processing
time, with values ranging from 0.4~ms for the simplest time-series and
smallest $\epsilon$, to 41.3~ms for the most complex time-series and
largest~$\epsilon$.
%~ Figure~\ref{fig:memory} shows the memory consumption
%~ of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
%~ at the end of long compressed ranges where the signal was $\epsilon$-closed
%~ to the linear approximation.

\paragraph{2D vs 3D}
For a given $\epsilon$, the compression
ratios are always higher in 2D than in 3D. It makes sense since the
probability for the signal to deviate from a straight line
approximation is higher in 3D than it is in 2D. Besides, resource
consumption is higher in 3D than in 2D: for the infinity norm, 3D
consumes 1.4 times more memory than 2D (1.8 times on average for
Euclidean norm), and processing time is 1.35 longer (1.34 on
average for Euclidean norm).
